ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-09-25 paper/body.tex
author response

We perform benchmarks on eight datasets from different domains. From the credit and finance domain we include three tabular datasets: Give Me Some Credit (\textit{GMSC})~\citep{kaggle2011give}, \textit{German Credit}~\citet{hoffman1994german} and \textit{California Housing}~\citet{pace1997sparse}. All of these are commonly used in the related literature~\citep{karimi2020survey,altmeyer2023endogenous,pawelczyk2021carla}. Following~\citet{schut2021generating} we also include two image datasets: \textit{MNIST}~\citep{lecun1998mnist} and \textit{Fashion MNIST}~\citep{xiao2017fashion}. Detailed descriptions and results for all datasets can be found in the appendix.

>>>>

We perform benchmarks on eight datasets from different domains. From the credit and finance domain we include three tabular datasets: Give Me Some Credit (\textit{GMSC})~\citep{kaggle2011give}, \textit{German Credit}~\citet{hoffman1994german} and \textit{California Housing}~\citet{pace1997sparse}. All of these are commonly used in the related literature~\citep{karimi2020survey,altmeyer2023endogenous,pawelczyk2021carla}. Following related literature~\citep{schut2021generating,dhurandhar2018explanations} we also include two image datasets: \textit{MNIST}~\citep{lecun1998mnist} and \textit{Fashion MNIST}~\citep{xiao2017fashion}. Detailed descriptions and results for all datasets can be found in the appendix.
